\cvsection{Experience}
\begin{cventries}
\cventry{
	    Lead Developer - Client Reference Data
    }
    {Vice President | Reference Data Technology | Scala Developer}
    {Bank of America | Singapore}
    {Feb 2020 - Current}
    {
      \begin{cvitems}
        \item {Built application to source counterparty ISDA regulatory protocol adherence information from Markit into enterprise client reference data application.}
        \item {Developed application to subscribe and relay time-sensitive client reference data events from enterprise system to legacy systems.}
        \item {Mentored junior developers and interns in software development best practices and domain knowledge.}
      \end{cvitems}
    }
\cventry{
      Senior Developer - Client Reference Data
    }
    {Assistant Vice President | Reference Data Technology | Scala Developer }
    {Bank of America | Singapore}
    {Feb 2016 - Jan 2020}
    {
      \begin{cvitems}
        \item {Built Scala application to generate and publish broker-to-client assigned numbers (BCAN) for China connect investment banking clients to Hong Kong stock exchange.}
        \item {Enhanced enterprise client reference data graph database and built business process workflows, using internal BPM framework and Scala, to maintain client regulatory attributes.}
        \item {Improved existing business process workflows to automate resolution of most common user queries.}
      \end{cvitems}
    }
\cventry{
	    Technology Analyst - Product Reference Data
    }
    {Officer | Reference Data Technology | Java, PLSQL Developer}
    {Bank of America | Singapore}
    {July 2013 - Jan. 2016}
    {
      \begin{cvitems}
        \item {Onboarded Japanese equities feeds into enterprise product reference data application to minimize data quality issues for front office applications.}
        \item {Developed utility tool using Java and Spring to compute data ownership distribution (etymology) for enterprise product reference data equities attributes.}
        \item {Built data quality reconciliation reports using Java and PLSQL to address data gaps for APAC markets.}
      \end{cvitems}
    }
\end{cventries}
